Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
moved large web inequalities into the main body, only one appendix now

@@

    \section{Large Triangle Structure Inequalities}
    \label{sec:web_inequalities}
    \subsection{Web Inflation Inequality}
    \label{sec:web_inequality}
    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{center}
        \vspace{-0.2in}
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{center}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
    \subsection{Symmetric Web Inflation Inequality}
    \label{sec:symmetic_web_inequality}
    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{center}
        \vspace{-0.2in}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{center}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
    \[ \bs{P(113)P(330)}_3 = P(113)P(330) + P(131)P(303) + P(311)P(033) \]

>>>>

    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{equation}
        \label{sec:web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{equation}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{equation}
        \label{sec:symmetic_web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{equation}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
    \[ \bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033) \]

@@
